% Tailored CV for Graphcore - Graduate Firmware Engineer
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\renewcommand{\sfdefault}{lmss}
\usepackage[scale=0.85]{geometry}
\usepackage{enumitem}
\setlist{noitemsep, leftmargin=*}

% Personal Information (kept consistent with master CV)
\name{Glen}{Muthoka Mutinda}
\phone{+44 7341 625286}
\email{theglenmuthoka@gmail.com}
\social[linkedin]{glenmuthoka}
\social[github]{Bananz0}
\address{Bristol, UK}{}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Final-year Electrical \& Electronics Engineering student with hands-on embedded systems, digital design and low-level software experience. Strong foundation in C/C++, SystemVerilog and real-time systems developed through space-grade CubeSat firmware, FPGA designs and IC tape-out projects. Currently researching AI-driven optical authentication using GPU-accelerated Python. Comfortable working across hardware and software boundaries to deliver reliable, testable firmware for complex platforms.}

\section{Education}
\cventry{2023--2026}{BEng Electrical \& Electronics Engineering (Expected First Class)}{University of Southampton}{Southampton, UK}{}{Key modules: Embedded Systems, Integrated Circuit Design, Digital Systems, Control Systems.\\
\textbf{Second Year Project:} TSMC 65nm IC Design \& Fabrication (Team Lead).\\
\textbf{Final Year Project:} AI-Driven Optical Authentication Framework using Optical PUFs (Lead Researcher).}

\section{Selected Experience}
\cventry{Sep 2023--Jun 2025}{Junior Software Engineer}{ARTEMIS Small Sat-1 Lunar CubeSat Project}{University of Southampton}{}{
\begin{itemize}
  \item Developed flight firmware in C/C++ for a lunar CubeSat; reduced system latency by 6\% via algorithmic optimisation and refactoring.
  \item Implemented unit testing frameworks and automated debugging procedures, increasing system reliability by 20\%.
  \item Designed and validated real-time telemetry processing and ground-station interfaces; practiced disciplined code reviews using MISRA-like guidelines.
\end{itemize}}

\cvitem{TSMC 65nm CPU Design}{Led a 6-member IC design project from RTL through physical verification to GDSII submission for fabrication. Verified timing and power constraints using SPICE simulations and performed DRC/LVS checks. Demonstrated cross-disciplinary hardware/software integration awareness.}

\cvitem{WattsApp (ESP32) --- Embedded Firmware}{Implemented embedded C firmware for an ESP32-based energy management system. Managed sensor integration (I2C/SPI/ADC), MQTT/Modbus communications, and reliable power measurement routines.}

\cvitem{WinStream --- Kernel / Driver Development}{Developed a Windows virtual audio device and low-level components for system-wide audio capture; experience navigating kernel-mode development challenges and low-latency requirements.}

\cvitem{FPGA Real-Time DSP}{Designed SystemVerilog FIR notch filter on Altera Cyclone platform with deterministic latency (real-time audio processing). Familiar with timing closure, synthesis and simulation flows.}

\section{Relevant Projects}
\cvitem{Galaxy Book Enabler}{System-level tooling (PowerShell) that manipulates hardware profile and OS configuration; demonstrates deep OS/firmware interaction knowledge and careful packaging/auto-update behaviour.}
\cvitem{eGPU Auto-Enabler}{Background Windows service for PnP device monitoring and power management; highlights reliability engineering and device lifecycle handling.}

\section{Technical Skills}
\cvitem{Languages}{C (embedded), C++, SystemVerilog, Python, PowerShell}
\cvitem{Embedded / Firmware}{RTOS concepts, real-time telemetry, MCU (ESP32/STM32 basics), low-level peripherals (I2C, SPI, UART, ADC), unit testing for firmware}
\cvitem{Hardware / Tools}{FPGA flows (Quartus/Vivado), IC design flow concepts (Cadence/Calibre familiarity), LTSpice/ModelSim}
\cvitem{Software Practices}{Continuous Integration, Git, automated testing, build systems (Make/CMake), code reviews, MISRA-aware C practices}
\cvitem{OS / Drivers}{Experience with kernel-mode concepts and device driver interactions; system-level troubleshooting on Windows and Linux}

\section{Awards \& Memberships}
\cvitem{}{Member, IEEE; Active open-source contributor with multiple projects demonstrating system-level and embedded expertise.}

\section{Other}
\cvitem{Right to Work}{UK student visa (valid until 2026) — eligible for Graduate Route visa.}

\end{document}
