\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\renewcommand{\sfdefault}{lmss}
\usepackage[scale=0.85]{geometry}

% Personal Information
\name{Glen}{Muthoka Mutinda}
\phone{+44 7341 625286}
\email{theglenmuthoka@gmail.com}
\social[linkedin]{glenmuthoka}
\social[github]{Bananz0}

\begin{document}

\recipient{AMD Recruitment Team}{Cambridge, United Kingdom}
\date{\today}
\opening{Dear AMD Recruitment Team,}
\closing{Yours sincerely,}

\makelettertitle

I am writing to express my strong interest in the Graduate Silicon Design Engineer - Formal Verification position at AMD. As a final-year Electrical \& Electronics Engineering student at the University of Southampton with a deep-seated passion for digital logic and processor microarchitecture, I am eager to contribute to AMD’s Graphics IP Central Formal Verification Team.

My technical foundation aligns closely with the rigorous verification standards AMD maintains for next-generation GPU and AI designs. In my role as Team Lead for a \textbf{TSMC 65nm Integrated Circuit Design project}, I managed the complete flow from RTL to GDSII tape-out. This experience taught me the critical importance of specification-driven design and rigorous verification, where I performed extensive SPICE simulations and full physical validation (Calibre DRC/LVS) to ensure silicon success with zero violations.

Furthermore, my development of \textbf{MIPSquare++}, a cycle-accurate 5-stage pipelined processor simulator, has given me a refined understanding of microarchitectural hazards and functional correctness. I engineered comprehensive test suites to verify data forwarding, hazard detection, and pipeline flushing—essentially debugging complex "counterexamples" in code logic. Similarly, in designing a \textbf{16-stage FIR Notch Filter on FPGA}, I used SystemVerilog and ModelSim to verify deterministic latency and functional fidelity under tight timing constraints.

Working on the \textbf{ARTEMIS Lunar CubeSat mission} also sharpened my ability to verify safety-critical software. By implementing automated unit testing and debugging procedures that improved system reliability by 20\%, I learned to approach verification with the same collaborative and meticulous mindset that AMD values. I am particularly excited about the prospect of applying these skills to formal methods using industry-standard tools like JasperGold, and I am highly motivated to learn and contribute to AMD's innovative AI-driven verification technologies.

Thank you for your time and consideration. I look forward to the possibility of discussing how my technical background and commitment to execution excellence can support AMD’s verification goals.

\makeletterclosing

\end{document}
