\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\renewcommand{\sfdefault}{lmss} 
\usepackage[scale=0.85]{geometry}
\usepackage{enumitem}
\setlist{noitemsep, leftmargin=*}

% Personal Information
\name{Glen}{Muthoka Mutinda}
\phone{+44 7341 625286}
\email{theglenmuthoka@gmail.com}
\social[linkedin]{glenmuthoka}
\social[github]{Bananz0}

\begin{document}

\makecvtitle

\section{Professional Summary}
Final-year Electrical \& Electronics Engineering student with practical experience in the complete IC design flow, from RTL to GDSII tape-out on the TSMC 65nm process node. Proficient in physical verification (DRC/LVS), timing analysis, and embedded systems development. Proven ability to lead technical teams and deliver high-reliability hardware/software systems, demonstrated through a successful CPU tape-out and flight software development for a lunar CubeSat. Seeking an internship at TSMC to contribute to advanced semiconductor manufacturing and design enablement.

\section{Education}
\cventry{2023--2026}{BEng Electrical \& Electronics Engineering (Expected First Class Honours)}{University of Southampton}{Southampton, UK}{}{
\textbf{Key Modules:} Integrated Circuit Design, Digital Systems Design, Embedded Systems, Control Systems, Signal Processing\\
\textbf{Second Year Project:} TSMC 65nm IC Design \& Fabrication (Team Lead) -- \textit{Achieved zero DRC violations}\\
\textbf{Final Year Project:} AI-Driven Optical Authentication Framework using Optical PUFs}

\section{Relevant Technical Projects}

\cvitem{TSMC 65nm CPU Design: Complete IC Design \& Fabrication Flow}{Sep 2023--Jun 2024\\
\textbf{Role:} Team Lead | \textbf{Tools:} Cadence S-Edit, L-Edit, T-Spice, Mentor Calibre (DRC/LVS)\\
Led a 6-member team through the full custom IC design flow for a CPU on TSMC's 65nm process.
\begin{itemize}
    \item Designed CPU datapath and control logic from schematic to layout.
    \item Performed extensive SPICE simulations to verify setup/hold times and critical path timing.
    \item Conducted full physical verification including Design Rule Checking (DRC) and Layout vs. Schematic (LVS) validation using Calibre.
    \item Successfully submitted GDSII files for fabrication with zero DRC violations.
    \item Optimized layout to achieve 15\% area reduction through custom cell design and strategic floorplanning.
\end{itemize}}

\cvitem{16-Stage FIR Notch Filter for Real-Time Audio on FPGA}{Nov 2024--Dec 2024\\
\textbf{Platform:} Altera Cyclone V (DE1-SoC) | \textbf{Language:} SystemVerilog | \textbf{Tools:} Quartus Prime, ModelSim\\
Designed a parametrized FIR digital filter for real-time processing.
\begin{itemize}
    \item Implemented a 4-state FSM controller achieving 19-cycle latency (950ns) from ADC to DAC.
    \item Synthesized design utilizing 2,847 logic elements (5\% utilization) with verified timing closure.
\end{itemize}}

\cvitem{AI-Driven Optical Authentication Framework}{Sep 2025--Jun 2026\\
\textbf{Role:} Lead Researcher | \textbf{Tools:} Python, CUDA, NumPy\\
Developing a security framework using Optical Physical Unclonable Functions (OPUFs).
\begin{itemize}
    \item Engineering GPU-accelerated data processing pipelines for high-dimensional spectral data.
    \item Developing quantization algorithms to convert analog spectral features into cryptographic bitstreams.
\end{itemize}}

\cvitem{MIPSquare: MIPS Assembly Simulator}{2024\\
\textbf{Language:} C++ | \textbf{Focus:} Computer Architecture\\
Built a MIPS processor simulator implementing instruction decoding, register file management, and memory operations, demonstrating deep understanding of processor architecture.}

\section{Professional Experience}
\cventry{Sep 2023--Jun 2025}{Junior Software Engineer}{ARTEMIS Small Sat-1 Lunar CubeSat Project}{University of Southampton}{}{
\begin{itemize}
    \item Developed flight software in C/C++ for a lunar mission, adhering to strict reliability standards (MISRA C guidelines).
    \item Reduced system latency by 6\% and enhanced reliability by 20\% through rigorous unit testing and code refactoring.
    \item Collaborated in a multidisciplinary team to meet space-grade timing and safety requirements.
\end{itemize}}

\section{Technical Skills}

\subsection{IC Design \& Hardware}
\cvitem{IC Design}{TSMC 65nm Process, Cadence S-Edit/L-Edit/T-Spice, Mentor Calibre (DRC/LVS), GDSII Tape-out, SPICE Simulation}
\cvitem{Digital Design}{SystemVerilog, VHDL, FPGA (Altera Quartus Prime, Xilinx Vivado), ModelSim, Timing Analysis}
\cvitem{PCB Design}{KiCad, Autodesk EAGLE}

\subsection{Programming \& Embedded}
\cvitem{Languages}{C/C++, SystemVerilog, Python, MATLAB, Assembly (MIPS/ARM)}
\cvitem{Embedded}{ESP32, Raspberry Pi, RTOS concepts, I2C/SPI/UART protocols}

\subsection{Tools and Platforms}
\cvitem{OS/DevOps}{Linux (Ubuntu/Debian), Git, Docker, Bash Scripting}
\cvitem{General}{VS Code, MATLAB Simulink}

\section{Professional Memberships}
\cvitem{2024--Present}{Member, Institute of Electrical and Electronics Engineers (IEEE)}

\end{document}
