% Cover letter targeted at Graphcore - Graduate Firmware Engineer
\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\begin{document}

\begin{letter}{Hiring Team \\ Graphcore \\ Bristol}
\opening{Dear Firmware Hiring Team,}

I am writing to apply for the Graduate Firmware Engineer position in Bristol. I am an Electrical \& Electronics Engineering student at the University of Southampton (expected First Class Honours) with hands-on experience across embedded firmware, digital design and low-level software engineering. I am excited by Graphcore's mission to build next-generation AI compute and believe my cross-disciplinary background makes me a strong fit for your firmware team.

In recent roles I have:
\begin{itemize}
  \item Developed flight firmware in C/C++ for a lunar CubeSat project where I implemented real-time telemetry, stricter unit testing and MISRA-style code reviews to improve reliability and reduce latency.
  \item Led the RTL-to-GDSII flow on a TSMC 65nm CPU design as team lead, gaining deep appreciation for silicon constraints and hardware/software co-design.
  \item Built embedded firmware for ESP32-based systems (sensor integration, MQTT/Modbus), designed deterministic FPGA DSP blocks in SystemVerilog, and implemented low-latency kernel-mode components on Windows for audio streaming.
\end{itemize}

I have practical experience with continuous integration and automated testing workflows, build systems, and disciplined code review practices that I will bring to Graphcore's firmware development lifecycle. I enjoy collaborating across teams — from silicon designers to driver and systems engineers — and I am motivated to help ship robust firmware that enables high-performance AI hardware.

I am based in Southampton and hold a UK student visa valid until 2026 (eligible for the Graduate Route). I would welcome the opportunity to discuss how my background aligns with the team’s needs and contribute to Graphcore’s next-generation products.

Thank you for considering my application. I look forward to the possibility of contributing to Graphcore’s firmware efforts.

\closing{Kind regards,}
\vspace{1em}
\noindent Glen Muthoka Mutinda\\
\noindent +44 7341 625286 \\
\noindent theglenmuthoka@gmail.com

\end{letter}
\end{document}
